---
title: "R HW 02"
author: "YOUR NAME HERE"
date: "`r Sys.Date()`"
format: 
  html:
    self-contained: true
    toc: true
    toc_float: true
    number_section: false
    highlight: "tango"
    theme: "cosmo"
editor: visual
editor_options: 
  chunk_output_type: console
---

```{r}
#| label: load-packages
#| message: false
library(tidyverse)
library(palmerpenguins)
```

# Exercise 1

```{r}

```

# Exercise 2

```{r ex-2}


```

> YOUR ANSWER HERE

# Exercise 3

```{r ex-3}

```

> YOUR COMMENTS HERE

# Exercise 4

```{r ex-4}

```

> YOUR COMMENTS HERE

# Exercise 5

```{r ex-5}

```

> YOUR COMMENTS HERE

# Exercise 6

```{r}

```

> YOUR COMMENTS HERE

# Exercise 7

```{r}

```

> YOUR COMMENTS HERE

# Exercise 8

```{r}

```

> YOUR COMMENTS HERE

# Exercise 9

```{r}

```

> YOUR COMMENTS HERE

# Reflection prompts

*Respond to each of the following after you have completed all exercises in this assignment*

*(RP1): What were the main concepts covered in this assignment?*

> YOUR ANSWER HERE

*(RP2): What's one thing you understand better or can do more confidently after completing these exercises?*

> YOUR ANSWER HERE

*(RP3): Where did you experience the most difficulty or uncertainty? Describe where you got stuck, what you tried, and what ultimately helped—or what remains unresolved.*

> YOUR ANSWER HERE
