---
title: "Data Importing & Cleaning: Class Practice"
subtitle: "STAT 7500"
author: "Your name"
format:
  html:
    toc: true
    embed-resources: true
execute:
  warning: true
  message: false
---

+ Make sure this .qmd is placed in your STAT_7500 folder. 
+ Download cat-lovers.csv from Github and place it in the data subfolder
+ This .qmd uses the same cat-lovers data and hotel data as the slides.

```{r}
#| label: setup
library(tidyverse)
library(lubridate)

cat_lovers_raw <- read_csv("data/cat-lovers.csv")
```

## Practice 1: Diagnose before fixing

The following code produces a warning and does not calculate the intended mean:

```{r}
#| eval: false
cat_lovers_raw |>
  summarise(mean_cats = mean(number_of_cats, na.rm = TRUE))
```

1. Inspect the different responses to `number_of_cats` and how often each appears. What type is the column?
2. Find the original responses from Ginger Clark and Doug Bass. Propose a cleaning rule and identify any assumptions it requires.
3. Why doesn't `na.rm = TRUE` solve this problem?

```{r}
#| label: inspect-cat-responses

```

**Your observations and proposed rule:**


### After the discussion

Record the cleaning pipeline developed in class. Save the result as a new data set while also preserving `cat_lovers_raw`. Check the resulting type and whether the number of missing values changed.

```{r}
#| label: clean-cat-responses

```

## Practice 2: Change the display, preserve the counts

Make a **horizontal bar chart** of `handedness`, with the most common category at the top. 

Before coding, decide:

- Which axis should contain `handedness`?
- How will you order its levels?
- Where will the first level appear on that axis?

Use `fct_infreq()` and, if needed, `fct_rev()`. Add informative axis labels.

```{r}
#| label: handedness-plot

```

Check your plot against a frequency table.

```{r}
#| label: check-handedness-counts

```

**What changed about the presentation, and what stayed the same?**


## Practice 3: Repair the date pipeline

```{r}
#| label: read-hotels
hotels <- read_csv(
  "https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2020/2020-02-11/hotels.csv"
)
```

The pipeline below runs, but its arrival dates are stored as text. It is shown without executing so you can inspect and adapt it first.

```{r}
#| eval: false
hotels |>
  unite(
    col = arrival_date,
    arrival_date_year, arrival_date_month,
    arrival_date_day_of_month,
    sep = " "
  ) |>
  count(arrival_date) |>
  ggplot(aes(x = arrival_date, y = n, group = 1)) +
  geom_line()
```

1. Identify where the pipeline creates text rather than a date.
2. Predict whether converting that text to a date will change the counts, the order, or both.
3. Adapt the pipeline to parse the date and produce a chronologically ordered plot. Add axis labels.


```{r}
#| label: repair-hotel-dates

```

Check the parsed column's class, its earliest and latest dates, and whether parsing introduced missing values. You may save an intermediate data frame to make these checks easier.

```{r}
#| label: check-hotel-dates

```

**How do you know the revised result makes sense?**



